Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-02-08 ms.tex
minor adjustments and comments

\title[Rapid-response Bayesian sky localization]{Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates}
\author{Leo Singer and Larry Price}
\address{LIGO Laboratory, California Institute of Technology, Pasadena, CA 91125, USA}
\ead{\mailto{leo.singer@ligo.org}, \mailto{larry.price@ligo.org}}

@@

With \eref{eq:gaussian-fisher-matrix} in hand, we return to our particular signal model, \Eref{eq:signal-model}. The necessary partial derivatives are
%
\begin{eqnarray*}
    \frac{\partial \tilde h}{\partial \rho} &= e^{\imath (\gamma - \omega \tau)} \tilde u (\omega) \\
    \frac{\partial \tilde h}{\partial \gamma} &= \imath \, \rho \, e^{\imath (\gamma - \omega \tau)} \tilde u (\omega) \\
    \frac{\partial \tilde h}{\partial \tau} &= -\imath \, \omega \, \rho \, e^{\imath (\gamma - \omega \tau)} \tilde u (\omega).
\end{eqnarray*}
%
The Fisher matrix elements are
%
\begin{eqnarray*}
    \mathcal{I}_{\rho\rho} &= \int_0^\infty \frac{|\tilde u (\omega)|^2}{S(\omega)} \, \mathrm{d}\omega \\
	\mathcal{I}_{\gamma\gamma} &= \rho^2 \int_0^\infty \frac{|\tilde u (\omega)|^2}{S(\omega)} \, \mathrm{d}\omega \\
	\mathcal{I}_{\tau\tau} &= \rho^2 \int_0^\infty \frac{|\tilde u (\omega)|^2}{S(\omega)} \omega^2 \, \mathrm{d}\omega \\
	\mathcal{I}_{\gamma\tau} &= -\rho^2 \int_0^\infty \frac{|\tilde u (\omega)|^2}{S(\omega)} \omega \, \mathrm{d}\omega = \mathcal{I}_{\tau\gamma} \\
	\mathcal{I}_{\rho\gamma} &= \mathcal{I}_{\gamma\rho} = \mathcal{I}_{\rho\tau} = \mathcal{I}_{\tau\rho} = 0.
\end{eqnarray*}
%
If the waveform $\tilde u (\omega)$ is normalized such that $\mathcal{I}_{\rho\rho} = 1$, we can introduce the \textit{\ac{SNR}-weighted moments of angular frequency},
%
\begin{equation}\label{eq:angular-frequency-moments}
    \overline{\omega^k} =
        \left[ \int_0^\infty \frac{|\tilde u (\omega)|^2}{S(\omega)} \omega^k \, \mathrm{d}\omega \right]
        \left[ \int_0^\infty \frac{|\tilde u (\omega)|^2}{S(\omega)} \, \mathrm{d}\omega \right]
\end{equation}
%
Then, we have
%
\begin{eqnarray*}
	\mathcal{I} = \bordermatrix{
        ~ & \rho & \gamma & \tau \cr
        \rho & 1 & 0 & 0 \cr
        \gamma & 0 & \rho^2 & -\rho^2 \overline{\omega} \cr
        \tau & 0 & -\rho^2 \overline{\omega} & \rho^2 \overline{\omega^2}
    }.
\end{eqnarray*}

>>>>

\title[Rapid-response Bayesian sky localization]{Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates}
\author{Leo Singer and Larry R. Price}
\address{LIGO Laboratory, California Institute of Technology, Pasadena, CA 91125, USA}
\ead{\mailto{leo.singer@ligo.org}, \mailto{larryp@caltech.edu}}

@@

\marginpar{LP: these derivatives are trivial and so is putting them into fisher. Perhaps we should lose the derivatives and re-write Fisher so that the integral appears only once?  Better yet, write out the equation for the noise moments and then use that.}
With \eref{eq:gaussian-fisher-matrix} in hand, we return to our particular signal model, \Eref{eq:signal-model}. The necessary partial derivatives are
%
\begin{eqnarray*}
    \frac{\partial \tilde h}{\partial \rho} &= e^{\imath (\gamma - \omega \tau)} \tilde u (\omega) \\
    \frac{\partial \tilde h}{\partial \gamma} &= \imath \, \rho \, e^{\imath (\gamma - \omega \tau)} \tilde u (\omega) \\
    \frac{\partial \tilde h}{\partial \tau} &= -\imath \, \omega \, \rho \, e^{\imath (\gamma - \omega \tau)} \tilde u (\omega).
\end{eqnarray*}
%
The Fisher matrix elements are
%
\begin{eqnarray*}
    \mathcal{I}_{\rho\rho} &= \int_0^\infty \frac{|\tilde u (\omega)|^2}{S(\omega)} \, \mathrm{d}\omega \\
	\mathcal{I}_{\gamma\gamma} &= \rho^2 \int_0^\infty \frac{|\tilde u (\omega)|^2}{S(\omega)} \, \mathrm{d}\omega \\
	\mathcal{I}_{\tau\tau} &= \rho^2 \int_0^\infty \frac{|\tilde u (\omega)|^2}{S(\omega)} \omega^2 \, \mathrm{d}\omega \\
	\mathcal{I}_{\gamma\tau} &= -\rho^2 \int_0^\infty \frac{|\tilde u (\omega)|^2}{S(\omega)} \omega \, \mathrm{d}\omega = \mathcal{I}_{\tau\gamma} \\
	\mathcal{I}_{\rho\gamma} &= \mathcal{I}_{\gamma\rho} = \mathcal{I}_{\rho\tau} = \mathcal{I}_{\tau\rho} = 0.
\end{eqnarray*}
%
If the waveform $\tilde u (\omega)$ is normalized such that $\mathcal{I}_{\rho\rho} = 1$, we can introduce the \textit{\ac{SNR}-weighted moments of angular frequency},
%
\begin{equation}\label{eq:angular-frequency-moments}
    \overline{\omega^k} =
        \left[ \int_0^\infty \frac{|\tilde u (\omega)|^2}{S(\omega)} \omega^k \, \mathrm{d}\omega \right]
        \left[ \int_0^\infty \frac{|\tilde u (\omega)|^2}{S(\omega)} \, \mathrm{d}\omega \right]
\end{equation}
%
Then, we have
%
\begin{eqnarray*}
	\mathcal{I} = \bordermatrix{
        ~ & \rho & \gamma & \tau \cr
        \rho & 1 & 0 & 0 \cr
        \gamma & 0 & \rho^2 & -\rho^2 \overline{\omega} \cr
        \tau & 0 & -\rho^2 \overline{\omega} & \rho^2 \overline{\omega^2}
    }.
\end{eqnarray*}
